### 2024-08-03 conteudo/methods/methods.tex
change table to appendix

(MAYBE I SHOULD ADD A RESTRICTION ABOUT IGNORING AUTOMATED GENERATED CODE, such as DML folder)

The function pairs selected randomly following our methodology can be consulted in the Table
(CREATE TABLE AND ADD HERE).

CREATE TABLE AND ADD HERE.

>>>>

The function pairs selected randomly following our methodology can be consulted in the Appendix
(CREATE Appendix AND ADD HERE).
